Download data

### 2024-05-09 scripts/subsetDataforCrews.Rmd
fn for empirical

lapply( 
  teams_list[2], project_maker, 
  admu = admin_boundaries, 
  target_species = spp_needed, 
  blm_surf = blm_surf, 
  fs_surf = usfs_surf, 
  fire = fire_perimeters, 
  invasive = invasives, 
  total_change = change_intensity,  
  occurrences = occurrences, 
  roads = roads,  
  pSTZs = prov_stz, 
  seed_transfer = STZ
  )

plot(ob[["Bishop - P102079"]][["10"]])

>>>>

p <- '/media/steppe/hdd/EmpiricalSeedZones/data/geodata/rasters'
f <- file.path(p, list.files(p, pattern = 'tif$'))
eSTZs <- rast(f)
names(eSTZs) <- gsub('-.*tif$', '', basename(f))
eSTZs <- project(eSTZs, 'epsg:5070') 
eSTZs <- resample(eSTZs, example_rast)
rm(f, p)

lapply( 
  teams_list[13], project_maker, 
  admu = admin_boundaries, 
  target_species = spp_needed, 
  blm_surf = blm_surf, 
  fs_surf = usfs_surf, 
  fire = fire_perimeters, 
  invasive = invasives, 
  total_change = change_intensity,  
  occurrences = occurrences, 
  roads = roads,  
  pSTZs = prov_stz, 
  eSTZs = eSTZs, 
  seed_transfer = STZ 
  )

plot(eSTZs)
